---
title: "Abacavirinol"
author: "Arriana Roehl!"
date: "12/5/18"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
abac <-read.csv(file="abacavirinol.csv",header=TRUE)
```
```{r}
LBGTguys = filter(abac,LBGT=="yes")

Girls = filter(abac,sex=="F")

Guys = filter(abac,sex=="M")
DrugGuys = filter(abac,Ivdrug=="user")
```

# Introduction
<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. We will run various tests for each group in order to see if the drug works in order to prevent AIDS. There are various groups involved.  The groups are "abac", "DrugGuys", "Girls","Guys",and "LGBTguys". We will analyze each group in order to see if the drug actually works.


# Methods For Everybody

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

We will need to use a barchart, tabelperc, rowperc, and colperc in order to evaluate the results.We will also need to use the chisq.test(tabel1), chisqtestGC(tabel1),fisher.test(tabel1)in order to organize all of the numerical results.
Lastly, we will use the chisq.test(tabel1), chisqtestGC(tabel1), fisher.test(tabel1) to analyze all of the inferential results. 


#Results
<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results
The results for everybody vary depending on which graph is run. We will use barchart and determine if the drug works. We will also evaluate the numerical data to compare the infected with the non-infected along with who took a placebo and who actually took the drug. These tests will determine if it actually works or not.


### Graphical Descriptive Results
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment, data = abac, type = "percent")
```


Acording to this chart, it shows that the drug did work because the people who took the placebo got a higher number of individuals who got aids, and the people who took the drug did not.


### Numerical Descriptive Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
tabel1 <- xtabs(~infected + treatment, data = abac)
rowPerc(tabel1)
colPerc(tabel1)
```


According to this data,the people who took the drug had a much smaller number of people who got aids in comparision to the people who took the placebo. 


## Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(tabel1)
chisqtestGC(tabel1)
fisher.test(tabel1)
```

According to the fisher test, and all of the other tests run, it shows that that everybo0dy would be better off taking the drug if they did not want to get aids. The hypothesis is that the drug will work in this group. The p value is rejected.


# Discussion and Conclusion
We will reject the hypothesis because the drug works.  After reviewing all of the data, it appeared that the indviduals who took the placebo had a higher chance of getting aids.  In conclusion, for everybody it appeared that the drug worked.






#Methods For Girls

# Introduction
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
We will need to use a barchart, tabelperc, rowperc, and colperc in order to evaluate the results.We will also need to use the chisq.test(tabel1), chisqtestGC(tabel1),fisher.test(tabel1)in order to organize all of the numerical results.
Lastly, we will use the chisq.test(tabel1), chisqtestGC(tabel1), fisher.test(tabel1) to analyze all of the inferential results.


#Results
<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->


## Descriptive Results


For the girls in particular, we will run similar tests as above.  The difference here is that the data, infact, will show that the drug did not work for the girls.


### Graphical Descriptive Results
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+treatment, data = Girls, type = "percent")
```


These results for the girls show that the drug did not work.  A majority of the girls who took the drug actually got aids in comparision to the girls who did not take anything.  A majority of the girls who did not take anything, were actually less likely to get aids.


### Numerical Descriptive Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
tabel1 <- xtabs(~infected + treatment, data = abac)
rowPerc(tabel1)
colPerc(tabel1)
```


This shows that the drug did not work in the girls.  Again, the girls who took the placebo were actually greater in percentage and did not get aids, in comparision to the girls who did take the drug.


## Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(tabel1)
chisqtestGC(tabel1)
fisher.test(tabel1)
```

The hypothesis here is that the drug will work.


# Discussion and Conclusion
We will reject the hypothesis becauuse the data shows that in this group, the drug did not actually work. It is interesting becuase the drug did not work in this group, the girls.  It did tend to work for the group overall.






#Methods For Guys

# Introduction
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

We will need to use a barchart, tabelperc, rowperc, and colperc in order to evaluate the results.We will also need to use the chisq.test(tabel1), chisqtestGC(tabel1),fisher.test(tabel1)in order to organize all of the numerical results.
Lastly, we will use the chisq.test(tabel1), chisqtestGC(tabel1), fisher.test(tabel1) to analyze all of the inferential results.


#Results
<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results
The results for the guys will ultimately show that the drug will work.


### Graphical Descriptive Results
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph
that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+treatment, data = Guys, type = "percent")
```

These results show that for the guys, the drug did work.  A majority of those who took the drug, did not get aids.  A large majority of those who did not, did get aids.


### Numerical Descriptive Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
tabel1 <- xtabs(~infected + treatment, data = abac)
rowPerc(tabel1)
colPerc(tabel1)
```

The numbers show that a majority of the guys who did take the drug, were less likely to get aids.  The ones who did not, obtained higher numbers of getting aids.


##Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(tabel1)
chisqtestGC(tabel1)
fisher.test(tabel1)
```

The fisher test shows that the p value is 0.01683, therefore it is rejected.


# Discussion and Conclusion
This group was not much different than the others. Overall the drug did work for these guys, umlike in the girl group. There were various tests run, as used in all of the other groups in order to ultimatley reach this conclusion.






#Methods For lgbt guys
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Introduction
We will need to use a barchart, tabelperc, rowperc, and colperc in order to evaluate the results.We will also need to use the chisq.test(tabel1), chisqtestGC(tabel1),fisher.test(tabel1)in order to organize all of the numerical results.
Lastly, we will use the chisq.test(tabel1), chisqtestGC(tabel1), fisher.test(tabel1) to analyze all of the inferential results.


#Results
<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results
Here the results will take an interesting turn showing much different results for this group.
There will be a huge difference in the results of the LBGT guys who took the drug and the ones who did not.


### Graphical Descriptive Results
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+treatment, data = LBGTguys, type = "percent")
```


There is a large difference in the numbers with this group. Here is shows, that the a majority of the guys who took the drug actually got the aids and a majority of those who did not take it, ended up with a bigger number of who did not get aids.


### Numerical Descriptive Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
tabel1 <- xtabs(~infected + treatment, data = abac)
rowPerc(tabel1)
colPerc(tabel1)
```


This chart shows similar results to the chart above.  THe drug did not work, therefore the numbers display results showing that those who took the placebo were a smaller number.


## Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(tabel1)
chisqtestGC(tabel1)
fisher.test (tabel1)
```


It is less than .05 here showing that the drug did not work for this group.


# Discussion and Conclusion
This group was very interesting in comparison to the other groups. According to the bar chart and fisher test, it showed that the individuals who actually took the drug had a greater number of individuals who got aids.  This was likely very suprising to those who were running the test, because of course, the expected results were for the drug to work.






#Methods For Drug Guys
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Introduction
We will need to use a barchart, tabelperc, rowperc, and colperc in order to evaluate the results.We will also need to use the chisq.test(tabel1), chisqtestGC(tabel1),fisher.test(tabel1)in order to organize all of the numerical results.
Lastly, we will use the chisq.test(tabel1), chisqtestGC(tabel1), fisher.test(tabel1) to analyze all of the inferential results.


#Results
<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results
The results will be much different to the one above with the LGBT guys.  This one will show a significant difference between the groups above.


### Graphical Descriptive Results
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+treatment, data = DrugGuys, type = "percent")
```


The bar chart shows that the majority of the people who took the drug did not get aids and a majority of those who took the placebo did get aids. There is a significant difference between the two.


### Numerical Descriptive Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
tabel1 <- xtabs(~infected + treatment, data = abac)
rowPerc(tabel1)
colPerc(tabel1)
```


These results show that more of the people who took the drug did not get aids and a majority of those who took the placebo did get aids.


## Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(tabel1)
chisqtestGC(tabel1)
fisher.test (tabel1)
```


The p-value here is rejected as well.


# Discussion and Conclusion
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
The drug did work for this group. For all of the groups, it appeared that it was ultimately succesful for most of them. In regards to this one in particular, we ran all of the same tests as the previous groups and came up with this conclusion. With all of the groups studied, we can conclude that overall, the drug will be succesfull in most individuals.
